Tailored Spiral In-Out Spectral-Spatial Water Suppression Pulses for Magnetic Resonance Spectroscopic Imaging

### 2020-08-16 Manuscript/Introduction.tex
wording

\par Multidimensional parallel transmission \cite{Katscher:2003:Magn-Reson-Med:12509830,zhu2004parallel} has been widely investigated for applications including
reduced field-of-view imaging \cite{malik:mrm:2015,mooiweer:2016},
transmit field ($B_1^+$) inhomogeneity compensation \cite{Zhang:2007:Magn-Reson-Med:16526012,cloos:kpstd:2012},
and compensation of susceptibility-induced signal loss \cite{deng:2009}.
One of the first algorithms developed to demonstrate the concept of parallel transmission was formulated in the k-space domain \cite{Katscher:2003:Magn-Reson-Med:12509830}.
In that method, a dense system matrix was constructed by Fourier transforming each transmit coil's $B_1^+$ map,
forming a 2D convolution matrix for each coil, and then concatenating the coils' convolution matrices.
The target pattern was also Fourier transformed and the pulses were solved by regularized pseudoinverse of the system matrix. 
A spatial domain formulation \cite{Grissom:2006:MRM} was proposed soon after,
wherein a non-uniform discrete Fourier transform matrix is constructed, 
duplicated for each transmit coil, and weighted by that coil's $B_1^+$ map.
The weighted matrices are concatenated and the pulses are solved by regularized pseudoinverse of the system matrix
or using an iterative method.
The spatial domain method is mathematically straightforward 
and enables flexible system modeling, 
incorporation of regions of interest and off-resonance compensation,
and the use of non-uniform fast Fourier transforms to accelerate matrix multiplies.
Since its introduction, nearly all parallel transmit studies have used the spatial domain method.

>>>>

\par Multidimensional parallel transmission \cite{Katscher:2003:Magn-Reson-Med:12509830,zhu2004parallel} has been widely investigated for applications including
reduced field-of-view imaging \cite{malik:mrm:2015,mooiweer:2016},
transmit field ($B_1^+$) inhomogeneity compensation \cite{Zhang:2007:Magn-Reson-Med:16526012,cloos:kpstd:2012},
and compensation of susceptibility-induced signal loss \cite{deng:2009}.
One of the first algorithms developed to demonstrate the concept of parallel transmission was formulated in the k-space domain \cite{Katscher:2003:Magn-Reson-Med:12509830}.
In that method, a dense system matrix was constructed by Fourier transforming each transmit coil's $B_1^+$ map,
forming a 2D convolution matrix for each coil, and then concatenating the coils' convolution matrices.
The target pattern was also Fourier transformed and the pulses were solved by regularized pseudoinverse of the system matrix. 
A spatial domain formulation \cite{Grissom:2006:MRM} was proposed soon after,
wherein a non-uniform discrete Fourier transform matrix is constructed, 
duplicated for each transmit coil, and weighted by that coil's $B_1^+$ map.
The weighted matrices are concatenated and the pulses are solved by regularized pseudoinverse of the system matrix
or using an iterative method.
The spatial domain method is mathematically straightforward 
and enables flexible modeling and compensation of effects such as off-resonance, 
incorporation of regions of interest,
and the use of non-uniform fast Fourier transforms to accelerate matrix multiplies.
Since its introduction, nearly all parallel transmission studies have used the spatial domain method.
